{\fontfamily{ptm}\selectfont The Proximal Point interpretation of Nesterov accelerated proximal gradient}

### 2024-08-23 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, changes

\section{Preliminaries}\label{sec:preliminaries}
    In this section we introduce the a descent lemma for Proximal Point Method (PPM) in the convex case. 
    We define the proximal gradient mapping $\mathcal T_L$, and gradient mapping $\mathcal G_L$ for function satisfying 
    \hyperref[assumption:smooth-nonsmooth-sum]
    {assumption \ref*{assumption:smooth-nonsmooth-sum}}. 
    A lower bound function is identified using the gradient mapping operator and proved in
    \hyperref[lemma:grad_map_linearization]{lemma \ref*{lemma:grad_map_linearization}}, 
    this is a key component of the proximal point interpretation of the accelerated gradient method. 
    \begin{assumption}\label{assumption:smooth-nonsmooth-sum}
        Let $h = f + g$ where $f, g$ are convex and $f$ is Lipschitz-Smooth. 
    \end{assumption}

@@

    \begin{definition}[The gradient mapping]
        \label{def:gradient_mapping}
        Suppose $h = f + g$ satisfies 
        \hyperref[assumption:smooth-nonsmooth-sum]{assumption \ref*{assumption:smooth-nonsmooth-sum}}. 
        Define the proximal gradient operator
        $$
            \mathcal T_L(x) := \hprox_{L^{-1}g}(x - L^{-1}\nabla f(x)),
        $$
        and the gradient mapping operator
        $$
            \mathcal G_L(x) = L(x - \mathcal T_L(x)). 
        $$
    \end{definition}
    \begin{remark}
        The name ``gradient mapping" comes from \cite[(2.2.54)]{nesterov_lectures_2018}, however, Nesterov was referring to only the case when $g$ is an indicator function of a convex set in his writing. 
        Of course, in Amir Beck \cite[10.3.2]{beck_first-order_nodate}, it has the exact same definition for gradient mapping as the above. 
    \end{remark}

    \begin{lemma}[Gradient mapping approximates subgradient]
    \label{lemma:grad-map-approx-subgrad}\; \\
        Suppose $h = f + g$ satisfies 
        \hyperref[assumption:smooth-nonsmooth-sum]{assumption \ref{assumption:smooth-nonsmooth-sum}}, 
        let $\mathcal T_L, \mathcal G_L$ be given by 
        \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}.
        Then for all $x$, the gradient mapping verifies
        \begin{align*}
            x^+ &= \mathcal T_L(x), 
            \\
            \mathcal G_L(x) = L(x - x^+) &\in  \nabla f(x) + \partial g(x^+). 
        \end{align*}
    \end{lemma}
    \begin{proof}
        Using the resolvent definition of the proximal gradient operator and the fact that the single-valuedness in the convex settings, $x^+$ has relations: 
        \begin{align*}
            x^+ &= [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f](x)
            \\
            [I + L^{-1}\partial g](x^+) &\ni [I - L^{-1}\nabla f](x)
            \\
            x^+ + L^{-1}\partial g(x^+) &\ni x - L^{-1}\nabla f(x)
            \\
            x^+ - x + L^{-1}\partial g(x^+) &\ni L^{-1}\nabla f(x)
            \\
            L(x^+ - x) + \partial g(x^+) &\ni - \nabla f(x)
            \\
            L(x - x^+) &\in \nabla f(x) + \partial g(x^+)
            \\
            \mathcal G_L(x) &\in \nabla f(x) + \partial g(x^+). 
        \end{align*}
    \end{proof}

@@

        \hyperref[assumption:smooth-nonsmooth-sum]{assumption \ref*{assumption:smooth-nonsmooth-sum}}, 

@@

        \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}. 

@@

\section{The PPM interpreation of accelerated gradient}\label{sec:ppm_interp_of_ag}
    In this section, we present the generic PPM formulation of the accelerated proximal gradient method. 
    This is general form presents us with a set of undetermine stepsize parameters $\eta_i, \tilde \eta_i$ that can be changed later to accomodate proofs that take Lypunov functions and phrase the convergence rate using the stepsizes sequence $\tilde \eta_i$. 
    These interpretations are extension in the non-smooth context of Ahn and Sra's work \cite{ahn_understanding_2022} using the proximal gradient mapping operator. 
    The next definition will start the discussion. 
    \begin{definition}[Linear lower bounding function]\label{def:gradmap-linear-lowerbnd-fxn}
        Let $h = f+ g$ satisfies
        \hyperref[assumption:smooth-nonsmooth-sum]{definition \ref*{assumption:smooth-nonsmooth-sum}}, 
        $\mathcal G_L$ given by 
        \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}. 
        Define for all $y$ the function
        \begin{align*}
            l_h(x; y) = h(\mathcal T_L y) + \langle \mathcal G_L(y), x - y \rangle 
            + \frac{L}{2}\Vert y - \mathcal T_L y\Vert^2. 
        \end{align*}
    \end{definition} 
    \begin{remark}
        The function satisfies $l_h(x; y) \le h(x)$ for all $x \in \RR, y \in \RR$ by 
        \hyperref[lemma:grad_map_linearization]
        {lemma \ref*{lemma:grad_map_linearization}}. 
    \end{remark}
    \par
    With the above definition, it's possible to formulate a generic form of accelerated gradient method using $l_h(x,y)$ as two proximal point methods anchored at some iterates $x_t, x_{t + 1}$.
    The formulation is generic because of undetermined stepsize parameter $\eta_t, \tilde \eta_t$ from the two proximal point. 
    \par
    We state the PPM interpretation of accelerated gradient in 
    \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}, 
    which has the equivalent form as presented in
    \hyperref[def:ag_prox_grad_generic]
    {definition \ref*{def:ag_prox_grad_generic}}. 
    \hyperref[prop:derive_ag_prox_grad_tript]
    {Proposition \ref*{prop:derive_ag_prox_grad_tript}} 
    shows their equivalence. 
    \par
    Throughout this section, we assume 
    \begin{enumerate}
        \item $h=f + g$ satisfies 
            \hyperref[assumption:smooth-nonsmooth-sum]
            {assumption \ref*{assumption:smooth-nonsmooth-sum}}, 
        \item Using $h$ as given from above, let $\mathcal T_L, \mathcal G_L$ be given by 
            \hyperref[def:gradient_mapping]
            {definition \ref*{def:gradient_mapping}}. 
        \item Using all above, let $l_h$ be given by 
            \hyperref[def:gradmap-linear-lowerbnd-fxn]
            {definition \ref*{def:gradmap-linear-lowerbnd-fxn}}. 
    \end{enumerate}

    \begin{definition}[AG proximal gradient PPM generic form]
    \label{def:ag_prox_grad_ppm}
        Define $\eta_t, \tilde \eta_t$ to be $> 0$ for all $t \in \N$. 
        With initial iterate $x_0, y_0$, 
        The generic form has iterates $x_t, y_t$ for all $t \in \N$ that satisfy: 
        $$
        \begin{aligned}
            x_{t + 1} &= \argmin_{x} \left\lbrace
                l_h(x; y_t) + \frac{1}{2\tilde \eta_{t + 1}} 
                \Vert x - x_t\Vert^2
            \right\rbrace,
            \\
            y_{t + 1}&= 
            \argmin_{x}
            \left\lbrace
                l_h(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
                \frac{1}{2\eta_{t + 1}} \Vert x - x_{t + 1}\Vert^2
            \right\rbrace.
        \end{aligned}
        $$

    \end{definition}

@@

    \begin{proposition}
    \label{prop:derive_ag_prox_grad_tript}
       We have equalities
        \begin{align*}
            x_{t + 1} &= \argmin_{x}
            \left\lbrace
                l_h(x, y_t) + \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
            \right\rbrace
            \\
            &= x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t), 
            \\
            y_{t + 1} &= \argmin_{x}
            \left\lbrace
                    h(y_t^+) + \langle \mathcal G_L(y_t), x - y_t\rangle + \frac{L}{2}\Vert x -y_t\Vert^2 + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
            \right\rbrace
            \\
            &= (1 + L\eta_{t + 1})^{-1}
            (x_{t + 1} + L\eta_{t + 1}(y_t - L^{-1}\mathcal  G_L(y_t))). 
        \end{align*}
        This thows
        \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}
        and 
        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}} 
        are equivalent. 
    \end{proposition}
    \begin{proof}
        Let $y_t^+ = \mathcal T_L(y_t)$, recall that $l_h(x; y_t) = h(y_t^+) + \langle \mathcal G_L(y_t), x -y_t\rangle \le f(x)$ by 
        \hyperref[lemma:grad_map_linearization]
        {lemma \ref*{lemma:grad_map_linearization}}
        Since $l_h(x; y_t)$ is a simple linear function wrt $x$, minimizing the quandratic where to get $x_{t + 1} = x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t)$; for $y_{t + 1}$, complete the square on the second and the third terms: 
        \begin{align*}
            & \frac{L}{2}\left(
                2\langle L^{-1}\mathcal G_L(y_t), x - y_t\rangle + 
                \Vert x - y_t\Vert^2
            \right)
            \\
            &= 
            \frac{L}{2}
            \left(
                - \Vert L^{-1} \mathcal G_L(y_t)\Vert^2  
                + \Vert L^{-1} \mathcal G_L(y_t)\Vert^2 
                + 
                2\langle L^{-1} \mathcal G_L(y_t), x - y_t\rangle + 
                \Vert x - y_t\Vert^2
            \right)
            \\
            &= \frac{L}{2}\left(
                - \Vert L^{-1}\mathcal G_L(y_t)\Vert^2  
                + \Vert x - (y_t - L^{-1}\mathcal G_L(y_t))
                \Vert^2
            \right), 
        \end{align*}
        therefore it transforms into 
        \begin{align*}
            y_{t + 1} &=\argmin_{x} \left\lbrace
                \frac{L}{2}\left\Vert 
                    x - (y_t - L^{-1}\mathcal G_L(y_t))
                \right\Vert^2
                + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
            \right\rbrace
            \\
            &=
            \frac{
                \left(y_t - L^{-1}\mathcal G_L(y_t)\right) + x_{t + 1}
            }{L + \eta_{t + 1}^{-1}}.
        \end{align*}
        Define $z_{t + 1} = y_t - \mathcal G_L(y_t) = \mathcal T_L(y_t)$, which is the proximal gradient set, then the above expression simplifies to 
        $$
        y_{t + 1} = (1 + L\eta_{t +1})^{-1}(x_{t + 1}+ L\eta_{t + 1}z_{t + 1}). 
        $$
    \end{proof}
    \begin{remark}
        $y_{t + 1}$ is the minimizer of a simple quadratic. 
        Given that the original function $h$ is potentially non-smooth, therefore it's not always an upper bound of $h(x)$. 
        The upper bound interpretation of the smooth case as proposed by Ahn \cite{ahn_understanding_2022}, Sra for the update of $y_{t + 1}$ fails when $h$ is non-smooth! 
    \end{remark}

\section{Generic Lyapunov analysis for accelerated gradient via PPM}
\label{sec:generic_ag_ppm_lyapunov_analysis}
    In this section we derive the generic convergence rate formuated by $\eta_i, \tilde \eta_i$. 
    \par
    The Lypunov function in 
    \hyperref[thm:generic_ag_convergence]{\ref*{thm:generic_ag_convergence}}
    is identical to Ahn and Sra 
    \cite[section 4.2]{ahn_understanding_2022}, 
    except for the involvement of the gradient mapping. 
    We adapated it into the context of proximal gradient by 
    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
    {lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}
    \par
    We present the convergence rate by compatifying results into 
    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
    {lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}} 
    to assist the proof of  
    \hyperref[thm:generic_ag_convergence]
    {Theorem \ref*{thm:generic_ag_convergence}} 
    which states new results that are extension to Ahn and Sra's works by introducing an error term to the Lypunov analysis, allowing for a weaker constraints for the stepsize paramters $\tilde \eta_i, \eta_i$ from 
    \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}. 
    \hyperref[thm:ag_generic_stepsize_constraints]{Theorem \ref*{thm:ag_generic_stepsize_constraints}}
    states the weakened constraints on the stepsize parameters $\tilde \eta_i, \eta_i$. 
    \par
    Throughout the section, we continue the assumption for $h = f + g$, gradient mapping $\mathcal G_L$ and proximal gradient mapping $\mathcal T_L$ from the previous section.

>>>>

\section{Preliminaries}\label{sec:preliminaries}
    In this section we introduce the a descent lemma for Proximal Point Method (PPM) in the convex case. 
    We define the proximal gradient mapping $\mathcal T_L$, and gradient mapping $\mathcal G_L$ for function satisfying 
    \hyperref[assumption:smooth-nonsmooth-sum]
    {assumption \ref*{assumption:smooth-nonsmooth-sum}}. 
    A lower bound function is identified using the gradient mapping operator and proved in
    \hyperref[lemma:grad_map_linearization]{Lemma \ref*{lemma:grad_map_linearization}}, 
    this is a key component of the proximal point interpretation of the accelerated gradient method. 
    \begin{assumption}\label{assumption:smooth-nonsmooth-sum}
        Let $h = f + g$ where $f, g$ are convex and $f$ is Lipschitz-Smooth. 
    \end{assumption}

@@

    \begin{definition}[The gradient mapping]
        \label{def:gradient_mapping}
        Suppose $h = f + g$ satisfies 
        \hyperref[assumption:smooth-nonsmooth-sum]{Assumption \ref*{assumption:smooth-nonsmooth-sum}}. 
        Define the proximal gradient operator
        $$
            \mathcal T_L(x) := \hprox_{L^{-1}g}(x - L^{-1}\nabla f(x)),
        $$
        and the gradient mapping operator
        $$
            \mathcal G_L(x) = L(x - \mathcal T_L(x)). 
        $$
    \end{definition}
    \begin{remark}
        The name ``gradient mapping" comes from \cite[(2.2.54)]{nesterov_lectures_2018}, however, Nesterov was referring to only the case when $g$ is an indicator function of a convex set in his writing. 
        Of course, in Amir Beck \cite[10.3.2]{beck_first-order_nodate}, it has the exact same definition for gradient mapping as the above. 
    \end{remark}

    \begin{lemma}[Gradient mapping approximates subgradient]
    \label{lemma:grad-map-approx-subgrad}\; \\
        Suppose $h = f + g$ satisfies 
        \hyperref[assumption:smooth-nonsmooth-sum]{Assumption \ref{assumption:smooth-nonsmooth-sum}}, 
        let $\mathcal T_L, \mathcal G_L$ be given by 
        \hyperref[def:gradient_mapping]{Definition \ref*{def:gradient_mapping}}.
        Then for all $x$, the gradient mapping verifies
        \begin{align*}
            x^+ &= \mathcal T_L(x), 
            \\
            \mathcal G_L(x) = L(x - x^+) &\in  \nabla f(x) + \partial g(x^+). 
        \end{align*}
    \end{lemma}
    \begin{proof}
        Using the resolvent definition of the proximal gradient operator and the fact that the single-valuedness in the convex settings, $x^+$ has relations: 
        \begin{align*}
            x^+ &= [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f](x)
            \\
            [I + L^{-1}\partial g](x^+) &\ni [I - L^{-1}\nabla f](x)
            \\
            x^+ + L^{-1}\partial g(x^+) &\ni x - L^{-1}\nabla f(x)
            \\
            x^+ - x + L^{-1}\partial g(x^+) &\ni L^{-1}\nabla f(x)
            \\
            L(x^+ - x) + \partial g(x^+) &\ni - \nabla f(x)
            \\
            L(x - x^+) &\in \nabla f(x) + \partial g(x^+)
            \\
            \mathcal G_L(x) &\in \nabla f(x) + \partial g(x^+). 
        \end{align*}
    \end{proof}

@@

        \hyperref[assumption:smooth-nonsmooth-sum]{Assumption \ref*{assumption:smooth-nonsmooth-sum}}, 

@@

        \hyperref[def:gradient_mapping]{Definition \ref*{def:gradient_mapping}}. 

@@

\section{The PPM interpreation of accelerated gradient}\label{sec:ppm_interp_of_ag}
    In this section, we present the generic PPM formulation of the accelerated proximal gradient method. 
    This is general form presents us with a set of undetermine stepsize parameters $\eta_i, \tilde \eta_i$ that can be changed later to accomodate proofs that take Lypunov functions and phrase the convergence rate using the stepsizes sequence $\tilde \eta_i$. 
    These interpretations are extension in the non-smooth context of Ahn and Sra's work \cite{ahn_understanding_2022} using the proximal gradient mapping operator. 
    The next definition will start the discussion. 
    \begin{definition}[Linear lower bounding function]\label{def:gradmap-linear-lowerbnd-fxn}
        Let $h = f+ g$ satisfies
        \hyperref[assumption:smooth-nonsmooth-sum]{Definition \ref*{assumption:smooth-nonsmooth-sum}}, 
        $\mathcal G_L$ given by 
        \hyperref[def:gradient_mapping]{Definition \ref*{def:gradient_mapping}}. 
        Define for all $y$ the function
        \begin{align*}
            l_h(x; y) = h(\mathcal T_L y) + \langle \mathcal G_L(y), x - y \rangle 
            + \frac{L}{2}\Vert y - \mathcal T_L y\Vert^2. 
        \end{align*}
    \end{definition} 
    \begin{remark}
        The function satisfies $l_h(x; y) \le h(x)$ for all $x \in \RR, y \in \RR$ by 
        \hyperref[lemma:grad_map_linearization]
        {Lemma \ref*{lemma:grad_map_linearization}}. 
    \end{remark}
    \par
    With the above definition, it's possible to formulate a generic form of accelerated gradient method using $l_h(x,y)$ as two proximal point methods anchored at some iterates $x_t, x_{t + 1}$.
    The formulation is generic because of undetermined stepsize parameter $\eta_t, \tilde \eta_t$ from the two proximal point. 
    \par
    We state the PPM interpretation of accelerated gradient in 
    \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}, 
    which has the equivalent form as presented in
    \hyperref[def:ag_prox_grad_generic]
    {Definition \ref*{def:ag_prox_grad_generic}}. 
    \hyperref[prop:derive_ag_prox_grad_tript]
    {Proposition \ref*{prop:derive_ag_prox_grad_tript}} 
    shows their equivalence. 
    \par
    Throughout this section, we assume 
    \begin{enumerate}
        \item $h=f + g$ satisfies 
            \hyperref[assumption:smooth-nonsmooth-sum]
            {Assumption \ref*{assumption:smooth-nonsmooth-sum}}, 
        \item Using $h$ as given from above, let $\mathcal T_L, \mathcal G_L$ be given by 
            \hyperref[def:gradient_mapping]
            {Definition \ref*{def:gradient_mapping}}. 
        \item Using all above, let $l_h$ be given by 
            \hyperref[def:gradmap-linear-lowerbnd-fxn]
            {Definition \ref*{def:gradmap-linear-lowerbnd-fxn}}. 
    \end{enumerate}

    \begin{definition}[AG proximal gradient PPM generic form]
    \label{def:ag_prox_grad_ppm}
        Define $\eta_t, \tilde \eta_t$ to be $> 0$ for all $t \in \N$. 
        With initial iterate $x_0, y_0$, 
        The generic form has iterates $x_t, y_t$ for all $t \in \N$ that satisfy: 
        $$
        \begin{aligned}
            x_{t + 1} &= \argmin_{x} \left\lbrace
                l_h(x; y_t) + \frac{1}{2\tilde \eta_{t + 1}} 
                \Vert x - x_t\Vert^2
            \right\rbrace,
            \\
            y_{t + 1}&= 
            \argmin_{x}
            \left\lbrace
                l_h(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
                \frac{1}{2\eta_{t + 1}} \Vert x - x_{t + 1}\Vert^2
            \right\rbrace.
        \end{aligned}
        $$
    \end{definition}

@@

    \begin{proposition}
    \label{prop:derive_ag_prox_grad_tript}
       We have equalities
        \begin{align*}
            x_{t + 1} &= \argmin_{x}
            \left\lbrace
                l_h(x, y_t) + \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
            \right\rbrace
            \\
            &= x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t), 
            \\
            y_{t + 1} &= \argmin_{x}
            \left\lbrace
                    h(y_t^+) + \langle \mathcal G_L(y_t), x - y_t\rangle + \frac{L}{2}\Vert x -y_t\Vert^2 + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
            \right\rbrace
            \\
            &= (1 + L\eta_{t + 1})^{-1}
            (x_{t + 1} + L\eta_{t + 1}(y_t - L^{-1}\mathcal  G_L(y_t))). 
        \end{align*}
        This thows
        \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}
        and 
        \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}} 
        are equivalent. 
    \end{proposition}
    \begin{proof}
        Let $y_t^+ = \mathcal T_L(y_t)$, recall that $l_h(x; y_t) = h(y_t^+) + \langle \mathcal G_L(y_t), x -y_t\rangle \le f(x)$ by 
        \hyperref[lemma:grad_map_linearization]
        {Lemma \ref*{lemma:grad_map_linearization}}
        Since $l_h(x; y_t)$ is a simple linear function wrt $x$, minimizing the quandratic where to get $x_{t + 1} = x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t)$; for $y_{t + 1}$, complete the square on the second and the third terms: 
        \begin{align*}
            & \frac{L}{2}\left(
                2\langle L^{-1}\mathcal G_L(y_t), x - y_t\rangle + 
                \Vert x - y_t\Vert^2
            \right)
            \\
            &= 
            \frac{L}{2}
            \left(
                - \Vert L^{-1} \mathcal G_L(y_t)\Vert^2  
                + \Vert L^{-1} \mathcal G_L(y_t)\Vert^2 
                + 
                2\langle L^{-1} \mathcal G_L(y_t), x - y_t\rangle + 
                \Vert x - y_t\Vert^2
            \right)
            \\
            &= \frac{L}{2}\left(
                - \Vert L^{-1}\mathcal G_L(y_t)\Vert^2  
                + \Vert x - (y_t - L^{-1}\mathcal G_L(y_t))
                \Vert^2
            \right), 
        \end{align*}
        therefore it transforms into 
        \begin{align*}
            y_{t + 1} &=\argmin_{x} \left\lbrace
                \frac{L}{2}\left\Vert 
                    x - (y_t - L^{-1}\mathcal G_L(y_t))
                \right\Vert^2
                + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
            \right\rbrace
            \\
            &=
            \frac{
                \left(y_t - L^{-1}\mathcal G_L(y_t)\right) + x_{t + 1}
            }{L + \eta_{t + 1}^{-1}}.
        \end{align*}
        Define $z_{t + 1} = y_t - \mathcal G_L(y_t) = \mathcal T_L(y_t)$, which is the proximal gradient set, then the above expression simplifies to 
        $$
        y_{t + 1} = (1 + L\eta_{t +1})^{-1}(x_{t + 1}+ L\eta_{t + 1}z_{t + 1}). 
        $$
    \end{proof}
    \begin{remark}
        $y_{t + 1}$ is the minimizer of a simple quadratic. 
        Given that the original function $h$ is potentially non-smooth, therefore it's not always an upper bound of $h(x)$. 
        The upper bound interpretation of the smooth case as proposed by Ahn \cite{ahn_understanding_2022}, Sra for the update of $y_{t + 1}$ fails when $h$ is non-smooth! 
    \end{remark}

\section{Generic Lyapunov analysis for accelerated gradient via PPM}
\label{sec:generic_ag_ppm_lyapunov_analysis}
    In this section we derive the generic convergence rate formuated by $\eta_i, \tilde \eta_i$. 
    \par
    The Lypunov function in 
    \hyperref[thm:generic_ag_convergence]{Theorem \ref*{thm:generic_ag_convergence}}
    is identical to Ahn and Sra 
    \cite[section 4.2]{ahn_understanding_2022}, 
    except for the involvement of the gradient mapping. 
    We adapated it into the context of proximal gradient by 
    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
    {Lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}
    \par
    We present the convergence rate by compatifying results into 
    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
    {Lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}} 
    to assist the proof of  
    \hyperref[thm:generic_ag_convergence]
    {Theorem \ref*{thm:generic_ag_convergence}} 
    which states new results that are extension to Ahn and Sra's works by introducing an error term to the Lypunov analysis, allowing for a weaker constraints for the stepsize paramters $\tilde \eta_i, \eta_i$ from 
    \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}. 
    \hyperref[thm:ag_generic_stepsize_constraints]{Theorem \ref*{thm:ag_generic_stepsize_constraints}}
    states the weakened constraints on the stepsize parameters $\tilde \eta_i, \eta_i$. 
    \par
    Throughout the section, we continue the assumption for $h = f + g$, gradient mapping $\mathcal G_L$ and proximal gradient mapping $\mathcal T_L$ from the previous section.
